{"latex_body":"The central claim of the Codynamic Book Machine is that a book is not produced by a single linear pass from outline to prose. It is produced by a coordinated system in which the outline, the agents, the dependency graph, the section artifacts, and the compiled outputs remain in motion together. Each part of the system both constrains and informs the others, so the project stays coherent while still allowing local revision.\n\nIn this sense, the machine is \emph{codynamic}: its components evolve together rather than in isolation. The outline is not merely a planning document; it is a live structural model that guides work allocation and records the intended shape of the book. Agents do not act as independent authors; they operate as specialized workers whose tasks are derived from that structure and whose outputs are checked against it. Dependencies are not hidden implementation details; they are explicit relationships that determine what can be drafted, revised, verified, or compiled next.\n\nThe same principle applies to artifacts. A section draft is not final text until it has been reconciled with the surrounding work object, the registered references, any required diagrams, and the build pipeline that turns source into publication output. When one artifact changes, the change can propagate through the rest of the system: a revised outline can alter section work, a new section draft can expose a missing dependency, a reference update can change citation keys, and a compilation failure can reveal a mismatch between source and generated output. The machine is designed to keep those feedback loops visible rather than suppress them.\n\nThis is the practical meaning of codynamic coordination. The system does not assume that intent, structure, prose, and publication are separate phases with clean handoffs. Instead, it treats them as coupled states of one evolving work. The outline expresses intent, the agents enact it, the dependencies preserve order, the artifacts record progress, and the compiled outputs verify that the whole remains buildable. By keeping those elements synchronized, the machine can support long-form writing without losing the relationship between plan, process, and result.\n\nThat coupling is also what makes the system resilient. If the book changes direction, the outline can be revised and the downstream work can be re-evaluated. If a section needs more evidence, the reference workflow can be brought into alignment before the prose is finalized. If a diagram or other media asset is required, the request can be routed into the same coordination fabric rather than handled as an afterthought. In each case, the machine preserves a single evolving project rather than a collection of disconnected files.\n\nA simple way to state the thesis is this: the Codynamic Book Machine works because it keeps the whole book in motion as a coordinated system. It does not merely generate text; it maintains the relationships that make the text trustworthy, buildable, and consistent with the author's intent. That is why the machine is best understood not as a pipeline with isolated stages, but as a codynamic system in which structure, labor, artifacts, and output continuously shape one another.","completeness_percent": 97,"completeness_rationale": "The revision preserves the strong existing thesis while tightening the final claim and improving flow from the prior section. It now more explicitly distinguishes the system from a simple pipeline and emphasizes the coupled evolution of outline, agents, dependencies, artifacts, and compiled outputs. The section is publishable as-is for its outline intent. A later pass could add a brief concrete example or a formal definition of codynamic behavior, but neither is required for this section."}
