This section records corrections, version history, limitations, and open problems for the present draft.

\begin{description}
  \item[Corrections.] Corrections are tracked as they are identified during drafting, review, and build verification. Each substantive change should record the affected location, the corrected statement, and the reason for the revision so that the manuscript remains auditable. When a correction changes a claim, definition, notation, dependency, or cross-reference elsewhere in the book, the corresponding downstream sections should be updated to preserve consistency. Minor typographical fixes may be noted briefly, while substantive mathematical or structural corrections should be described explicitly.

  \item[Version history.] The change log serves as a compact history of the section and, where relevant, the book-level draft. Each entry should include a version identifier, a date, and a concise summary of the changes introduced in that revision. Entries should be ordered chronologically so that the evolution of the manuscript can be reconstructed from the log alone.

  \item[Limitations.] The present draft is intentionally limited to the information currently available in the source material. It does not yet enumerate specific errata items, nor does it provide a complete release-by-release history. Any claim of completeness should therefore be read as provisional until the section is expanded with concrete entries. In particular, this text describes the intended maintenance policy rather than a finalized archive of corrections.

  \item[Open problems.] Open problems include unresolved technical issues, pending editorial questions, and any known gaps in coverage that remain after review. Each item should be listed explicitly when identified, together with a short note on whether the issue is conceptual, notational, computational, or bibliographic in nature. Where possible, each open problem should be paired with a proposed next step or a pointer to the section or chapter most directly affected.
\end{description}

For maintenance purposes, future entries in this section should distinguish between minor typographical fixes, substantive mathematical corrections, and unresolved limitations that may affect interpretation or implementation. When a limitation is resolved, it should be moved from the open-problems list into the correction history with a brief note on the resolution path.

The imported source material for this section is minimal and confirms only the intended categories: corrections, version history, limitations, and open problems. Accordingly, this draft preserves the maintenance policy in prose form and leaves concrete errata entries to future revisions.

\begin{description}
  \item[Tracked corrections.] No specific corrections have been recorded in the imported source material yet. When entries are added, each should identify the affected location, the corrected statement, and the downstream impact, if any.

  \item[Tracked version history.] No dated revision table is available in the current source material. A future log should include version identifiers, dates, and concise summaries of changes in chronological order.

  \item[Known limitations.] The present section is a placeholder for a fuller errata archive. It does not yet enumerate known issues, and it should not be read as a claim that the manuscript is free of defects.

  \item[Open problems.] Any unresolved issues should be listed here with enough detail to support follow-up. At minimum, each item should indicate whether it is conceptual, notational, computational, or bibliographic, and should point to the section or chapter most directly affected.
\end{description}
